Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-11 paper/paper.tex
Show confidence comparison

The average participant was 33.7 years old.
26 participants self-identified as male and 8 as female.
All participants reported that they had no technical problems with the study procedures.
Only 11\% of our participants said they are not with all of these visualization types: bar charts, scatter plots, and heatmaps.
On average participants spent 8 minutes on the study with 3:20 minutes standard deviation.
As expected, most participants spent more time on the questions than the visualizations and overall the most time on the questions about the precise data.

@@

>>>>

The average participant was 33.7 years old.
26 participants self-identified as male and 8 as female.
All participants reported that they had no technical problems with the study procedures.
Only 11\% of our participants said they are not with all of these visualization types: bar charts, scatter plots, and heatmaps.

@@

Participants completed the study (excluding instructions) in around 7:30 minutes (with a standard deviation of 3.27 minutes).
As expected, most participants spent more time on the questions than the visualizations and overall the most time on the questions about the precise data.

\figref{fig:confidence_approximate} shows the confidence of participants in their responses grouped by approximate and precise.

\begin{figure}[!t]
  \centering
  \includegraphics[width=0.8\columnwidth]{confidence}
  \caption{Relative counts of confidence in answers about the approximate and precise data. 1 is the lowest confidence, 7 the highest.}
  \label{fig:confidence}
\end{figure}
